Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-11 reproducing_registered_reports.Rmd
submission

author_note: |
  This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.

@@

@@

# Conflict of Interest Statement
One author (SG) worked at Code Ocean during the writing of this manuscript. SG joined the project after its accompanying Code Ocean component was already submitted and published, and did not write any of the text concerning Code Ocean.

>>>>

author_note: |
  This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.

@@

### Data

All data and the code used to create this manuscript is provided in an OSF repository at https://osf.io/suqz3/.

@@

# Author Contributions

P. Obels and D. Lakens developed the idea. All authors contributed data by reproducing analyses. P. Obels drafted the initial version of the manuscript, D. Lakens wrote the final version, all authors revised the manuscript.

# Conflict of Interest Statement

One author (SG) worked at Code Ocean during the writing of this manuscript. SG joined the project after its accompanying Code Ocean component was already submitted and published, and did not write any of the text concerning Code Ocean.

### 2019-09-11 reproducing_registered_reports.tex
submission

\authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.

@@

@@

>>>>

\authornote{This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.

@@

\hypertarget{data}{%
\subsubsection{Data}\label{data}}

All data and the code used to create this manuscript is provided in an OSF repository at \url{https://osf.io/suqz3/}.

@@

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

P. Obels and D. Lakens developed the idea. All authors contributed data by reproducing analyses. P. Obels drafted the initial version of the manuscript, D. Lakens wrote the final version, all authors revised the manuscript.
